### 2014-10-01 editaveis/msp430_circuito.tex
Draw tacometer circuit with tikz

%This is a port of the GNU C Compiler (GCC) and GNU Binutils (as, ld) for the embedded processor MSP430. Tools for debugging and download are provided (GDB, JTAG and BSL)
% subsection mspgcc (end)

\section{Circuito} % (fold)
\label{sec:circuito}

% section circuito (end)

>>>>

Is a port of the GNU C Compiler (GCC) and GNU Binutils (as, ld) for the embedded processor MSP430. Tools for debugging and download are provided (GDB, JTAG and BSL)

\section{Circuitos} % (fold)
\label{sec:circuito}

\subsection{Tacômetro} % (fold)
\label{sub:tac_metro}

% subsection tac_metro (end)
\begin{figure}[h]
	\centering
	\begin{circuitikz}[american,scale=0.7]

	\draw
	(2.5,0) node[short] (init) {}
	% (2.5,-11) node[ground] (g) {}
	(10,-11) node[ground] (g) {}
	(18.1,-5.7) node[op amp,yscale=-1] (opamp){}
	(opamp.+) node[left] {}
	(17.9,-5.7) node[open]  {$LM324$}
	(opamp.-) node[left] {}
	(opamp.out) --  ++(1,0) node[ocirc,o-*] {~$MSP430$}
	(opamp.up) to [short] (18,-11) to (g)
	(opamp.down) ++ (0,.5) node[above] {} -- (opamp.down)
	;

	\draw
	(g) to [short] (2.5,-11) to [battery1,l_=$5V$,n=cap,*-*] ++(0,11)  to (init)
	(init)  to[short, *-*] (18,0) to (opamp.down)  ++(3,-3)
	(init)  to[short, *-*] (5,0) to [R,l^=$100\Omega$] ++(0,-5) to [empty led,l^=$IF\_Emiter$,-*] (5,-11) to (g)
	(init)  to[short, *-*] (10,0) to [R,l^=$1K\Omega$] ++(0,-5) to [short,n=in1,*-*] ++(0,0) 
	(g) to [pD,l^=$IF\_Sensor$,*-,mirror] ++(0,5) to (in1)
	(in1) to (opamp.+)
	(init)  to[short, *-*] (15,0) to [R,l^=$10K\Omega$] ++(0,-5)  to [short] ++(0,-1.40)to [short,n=in2,-*] ++(0,0) to [R,l^=$10K\Omega$,-*] (15,-11) to (g)
	(in2) to (opamp.-)
	;

	\end{circuitikz}
	\caption[Tacômetro]{Circuito do Tacômetro}
	\label{circ}
\end{figure}
